Keep your Laziness in Check

### 2018-03-09 paper/main.tex
[paper] filled out some citations

Lazy evaluation gives tremendous power to functional programmers
~\cite{WhyFPMatters} and is actively used in various practical
applications. For instance, the big-data framework Spark uses laziness
to drive computations on demand\cn, Apple's programming language Swift
leverages it to initialize expensive resources as needed\cn, and many
functional reactive programming web frameworks rely on
it crucially\cn \leo{This point might need more exposition about frp}. Haskell
is the most popular programming language that allows programmers to
enjoy the power of lazy evaluation by default. However, it
does not come without a price.
\leo{Didn't we have an FRP quote by someone that Laziness was the third source of
bugs or something? Work that in?}
\hzh{Ryan Trinkle (author of Reflex) said laziness was the 3rd most difficult thing to
get right, but let's check with him on whether we can quote him on that.}

@@

In the next section we work through two more examples, functional
queues and functional maps, demonstrating both the difficulties of
programming with laziness and how our approach can be used to
alleviate them.
%
In the rest of the paper, we present our technical contributions:
\begin{itemize}
\item We introduce a novel approach to specifying the laziness behavior
of functions that is {\em precise} and {\em compositional}. Such
specifications are expressive enough to capture exactly how much
evaluation occurs within a data structure
%\leo{Also add
%drawbacks/partiality here? If not here, where in the intro?} \hzh{I'm
%not sure if we should bring in partiality (in the sense of
%divergence/nontermination) yet since that seems like a rather
%technical detail of the spec}
\item We propose a framework for automated testing against such specifications.\caleb{Automated testing? Can be more specific}\leo{Should we mention QuickCheck here?}
\item We improve upon the random function generators from QuickCheck\cn to generate functions with arbitrary laziness behaviors.
\item We discuss our generic programming-based impementation to apply StrictCheck to all algebraic data types.\leo{I guess ``packed'' maps do not qualified as algebraic?}
\end{itemize}
%
Section~\ref{sec:related} discusses related work. We conclude and draw
directions for future work in Section~\ref{sec:concl}.

@@

The \lk{Spec} type has a single constructor with the same name. This
constructor takes a higher-order function in
continuation-passing-style ~\cn, where the first argument to the
function is a framework-supplied function that takes the predicted
demand on the inputs. We will always name this argument \lk{predict}
in this paper. The function is CPS'd to hide some internal plumbing
that presents a variadic interface to the user, so that the number of
arguments to \lk{predict} always matches the length of the type-level
list in \lk{Spec}.

>>>>

Lazy evaluation gives tremendous power to functional programmers
~\cite{WhyFPMatters} and is actively used in various practical
applications. For instance, the big-data framework Spark uses laziness
to drive computations on demand
~\cite{Zaharia:2012:RDD:2228298.2228301}, Apple's programming language
Swift leverages it to initialize expensive resources as needed
~\cite{Swift}, and many functional reactive programming web frameworks
rely on it crucially\cn \leo{This point might need more exposition
about frp}. Haskell is the most popular programming language that
allows programmers to enjoy the power of lazy evaluation by
default. However, it does not come without a price.
\leo{Didn't we have an FRP quote by someone that Laziness was the third source of
bugs or something? Work that in?}
\hzh{Ryan Trinkle (author of Reflex) said laziness was the 3rd most difficult thing to
get right, but let's check with him on whether we can quote him on that.}

@@

In the next section we work through two more examples, functional
queues and functional maps, demonstrating both the difficulties of
programming with laziness and how our approach can be used to
alleviate them.
%
In the rest of the paper, we present our technical contributions:
\begin{itemize}
\item We introduce a novel approach to specifying the laziness behavior
of functions that is {\em precise} and {\em compositional}. Such
specifications are expressive enough to capture exactly how much
evaluation occurs within a data structure
%\leo{Also add
%drawbacks/partiality here? If not here, where in the intro?} \hzh{I'm
%not sure if we should bring in partiality (in the sense of
%divergence/nontermination) yet since that seems like a rather
%technical detail of the spec}
\item We propose a framework for automated testing against such specifications.\caleb{Automated testing? Can be more specific}\leo{Should we mention QuickCheck here?}
\item We improve upon the random function generators from QuickCheck ~\cite{Claessen:2000:QLT:357766.351266} to generate functions with arbitrary laziness behaviors.
\item We discuss our generic programming-based impementation to apply StrictCheck to all algebraic data types.\leo{I guess ``packed'' maps do not qualified as algebraic?}
\end{itemize}
%
Section~\ref{sec:related} discusses related work. We conclude and draw
directions for future work in Section~\ref{sec:concl}.

@@

The \lk{Spec} type has a single constructor with the same name. This
constructor takes a higher-order function in
continuation-passing-style ~\cite{Reynolds:1993:DC:198112.198114},
where the first argument to the function is a framework-supplied
function that takes the predicted demand on the inputs. We will always
name this argument \lk{predict} in this paper. The function is CPS'd
to hide some internal plumbing that presents a variadic interface to
the user, so that the number of arguments to \lk{predict} always
matches the length of the type-level list in \lk{Spec}.
